New modal operators for constructive mathematics

### 2023-09-14 slides-luminy2023.tex
typo

    By traveling the multiverse (upwards, keeping ties to the base), exploiting
    that \\
    -- \textsc{lem} holds \emph{somewhere} and \\
    -- \textsc{dc} holds \emph{proximally}.
  \end{enumerate}
\end{frame}

>>>>

    By traveling the multiverse (upwards, keeping ties to the base), exploiting
    that \\
    -- \textsc{lem} holds \emph{somewhere} and \\
    -- instances of \textsc{dc} holds \emph{proximally}.
  \end{enumerate}
\end{frame}
